Generate data for NOBA cod ensemble modeling

### 2020-06-01 NOBAcod.Rmd
try wrappers with new output

#### Age composition (age classes)
```{r agecomp-1}

@@

#### Survey weight at age (age classes)

```{r wtageclass-1}

@@

@@

Wrappers work for NOBA cod using standard age classes. Now to modify the underlying code to get full age structure.

@@

Update: there is now a fleet column in output but the function is still incomplete; will not work if more than one fleet per species.

@@

NOTE that the fleet column is lost in the `atlantiom::sample_fish` function!

@@

```{r testruntruth}

@@

>>>>

#### Survey age composition (age classes)
```{r agecomp-1}

@@

#### Survey weight at age (age classes)
```{r wtageclass-1}

@@

#### Fishery age composition (age classes)
```{r agecomp-1}

Natage <- filter(fish_age_comp, time %in% c(55:175))

@@

Wrappers work for NOBA cod using standard age classes.

Visualize new annual age output for numbers at age, catch at age, and weight at age (interpolated):

### Wrapper test results for annual ages {#annageoutput}{.tabset}

#### Survey age composition (annual ages)
```{r plot-annagecomp}

#### Survey weight at age (annual ages)
```{r plot-annwtage}

#### Fishery catch at age (annual ages)
```{r plot-catchagecomp}

# (Annage development details below)

Now to modify the underlying code to get full age structure.

@@

Update: there is now a fleet column in output which should index correctly if a species is caught by multiple fleets.

@@

NOTE that the fleet column is lost in the `atlantisom::sample_fish` function!

@@

```{r testruntruth, eval=FALSE}

@@

After much debugging to properly index multiple fleets per species in catch at annual age output, this produced a run_truth.Rdata file and took about 40 minutes to run.

Now all of the wrappers need to read from annage to produce composition data. `om_init()`  now takes annage flag from the config file. `om_species()` looks for annage bio and catch output in the truth file and includes it in the species file (adding NULL if it isn't there).

Also still need the weight at age interpolation function. Incorporate this at the `om_comps()` step. Next rmd!

Running om_init, om_species, om_index, om_comps in chunk above, plot the annage output [above](#annageoutput).
